%\setcounter{page}{2}

\cleardoublepage

\section*{Abstract}

%The function of the abstract is to summarize, in one or two paragraphs, the %major aspects of the entire bachelor or master thesis. It is usually written %after writing most of the chapters.

%It should include the following:
%\begin{itemize}
%	\item Definition of the problem (the question(s) that you want to answer) %and its purpose (Introduction).
%	\item Methods used and experiments designed to solve it. Try to describe it %basically, without covering too many details.
%	\item Quantitative results or conclusions. Talk about the final results in a %general way and how they can solve the problem (how they answer the %question(s)). 
%\end{itemize}

%Even if the Title can be a reference of the work's meaning, the Abstract should %help the reader to understand in a quick view, the full meaning of the work. 
%The abstract length should be around 300 words.

%Abstracts are protected under copyright law just as any other form of written %speech is protected. However, publishers of scientific articles invariably make %abstracts publicly available, even when the article itself is protected by a %toll barrier. For example, articles in the biomedical literature are available %publicly from MEDLINE which is accessible through PubMed. It is a common %misconception that the abstracts in MEDLINE provide sufficient information for %medical practitioners, students, scholars and patients[citation needed]. The %abstract can convey the main results and conclusions of a scientific article %but the full text article must be consulted for details of the methodology, the %full experimental results, and a critical discussion of the interpretations and %conclusions. Consulting the abstract alone is inadequate for scholarship and %may lead to inappropriate medical decisions[2].

%An abstract\cite{Ikeda1997, levensthein65:_binar, Middleton2002, salton89} %allows one to sift through copious amounts of papers for ones in which the %researcher can have more confidence that they will be relevant to his research. %Once papers are chosen based on the abstract, they must be read carefully to be %evaluated for relevance. It is commonly surmised that one must not base %reference citations on the abstract alone, but the entire merits of a paper.

Wireless Sensor Networks (WSN) are an emerging technology that enables new possibilities for localization and tracking. Radio Tomographic Imaging(RTI) is a localization technique that analyses the signal strength between nodes inside a WSN, making it possible to localize and track a person without it needing to carry any device.

To do this, a system that measures the signal strengths of each link inside a WSN is needed. The approaches suggested by the literature however assume that all the nodes inside a WSN can hear each other. This makes it impossible to apply the same solution to a WSN that covers large areas like a whole floor or a whole building. To make it possible to apply RTI to large environments, a new approach is necessary that is able to measure and collect the signal strength of each link in a WSN where not every node can hear all the other nodes. 

This thesis provides an approach for a self calibrating signal strength measurement system that takes into account that not all the nodes can hear each other, qualifying it to be deployable in large areas. To measure the signal strength, each node needs to send a message. The suggested approach creates a schedule that defines a predecessor and successor for every node inside the WSN. On the basis of this schedule the nodes are able to send messages and measure the signal strength in a synchronized way that avoids message collisions which would result in invalid measurements for the computation of the RTI. To collect the measurement from the WSN paths to a central point are defined in a calibration phase. 

The system is then tested in a WSN with 32 nodes that covers a whole floor with a size of $531 m^2$. These tests show that the suggested approach can take measurements quick enough to enable localization with RTI.
\cleardoublepage
